IN FOCUS \\ Natural history matters: how biological constraints shape diversified interactions in pollination networks

### 2016-07-05 ms_infocus.tex
Edits to intro section.

 Phenotypic fitting of corolla length and shape and pollinators' feeding apparatus and body sizes are important because the better the fit, the better the consequences in terms of fitness outcomes for the interaction partners \citep{Nilsson:1988}. Yet the expectation of perfect trait matching across populations or communities is too simplistic \citep{Anderson:2010}.

@@

>>>>

 Phenotypic fitting of corolla length and shape and the pollinators' feeding apparatus and body sizes are important because the better the fit, the better the consequences in terms of fitness outcomes for the interaction partners \citep{Nilsson:1988}. Yet the expectation of perfect trait matching across populations or communities is too simplistic \citep{Anderson:2010}: "arms races" as initially suggested by Darwin and Wallace are frequently asymmetric, originating pollinator shifts rather than tight phenotypic trait matching (Fig. 1). Extensive local variation in phenotypic mismatch exists in different plant-pollinator systems \citep[e.g., ][]{Cocucci:2009,Anderson:2010,More:2012}, with pollinator-mediated selection geographic mosaics of locally coevolved partners.

Recent work by Sazatornil \textit{et al.} \citep{Sazatornil:2016} provides evidences that the types of trait mismatching outlined in Fig. 1 limit the ranges of host plants for sphingid pollinators, and ultimately shape their complex plant-pollinator networks.

@@

\bibitem{More:2012}
Moré, M., Amorim, F.W., Benitez-Vieyra, S., Medina, A.M., Sazima, M. \& Cocucci, A.A. (2012) Armament Imbalances: Match and Mismatch in Plant-Pollinator Traits of Highly Specialized Long-Spurred Orchids (ed M Heil). PLoS ONE, 7, e41878.

\bibitem{Sazatornil:2016}
Sazatornil, F.D., Moré, M., Benitez-Vieyra, S., Cocucci, A.A., Kitching, I.J., Schlumpberger, B.O., Oliveira, P.E., Sazima, M. \& Amorim, F.W. (2016) Beyond neutral and forbidden links: morphological matches and the assembly of mutualistic hawkmoth-plant networks. Journal of Animal Ecology, 00, 000–000.
